Deep Gaussian Processes and Hierarchical Modeling with Functional Data: A Case Study in Cosmological Power Spectra

### 2024-06-05 paper/main.tex
add in toy sims & image

Here, we provide results from a simulation study comparing the GP and DGP models, in which case the true curve is known. \textcolor{blue}{I can include details for a sim study based on simulated data I construct, or I can use the dataset Dave mentioned getting to use here.}

>>>>

Here, we provide results from a simulation study comparing the GP and DGP models, in which case the true curve is known. Following \cite{moran2024dpc}, we consider two functions (1 and 2) each with three variance specifications (settings ``A", ``B", ``C"). Our mean squared error (MSE) results are seen in Figure \ref{fig:collect_sims}; our DGP-HM model outperforms these current benchmark methods. \textcolor{blue}{We can also include a setting ``D", where the underlying error covariance has spatial dependence (e.g., noise with a Mat'ern covariance). Additionally, we can look at linear theory simulations.}

\begin{figure}[ht]
    \centering
    \includegraphics[width=6in]{collect_sims.png}
    \caption{Average MSE of our method across all $k$ values. \textcolor{blue}{Add competitors.}}
    \label{fig:collect_sims}
\end{figure}
